Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-10 ms/ms/ms.Rmd
<edit ms>

Reproducibility—the ability to recompute results—and replicability—the chances other experimenters will achieve a consistent result—are two foundational characteristics of successful scientific research (Leek and Peng 2015). The analysis code associated with this project can be accessed through the [Supplementary Materials](https://seldenlab.github.io/elliptical.bifaces/), is available through the GitHub repository [https://github.com/seldenlab/elliptical.bifaces](https://github.com/seldenlab/elliptical.bifaces), and digitally curated on the Open Science Framework [DOI 10.17605/OSF.IO/PH25W](https://osf.io/ph25w/). The reproducible nature of this enterprise provides a means for others to critically assess and evaluate the various analytical components (Gray and Marwick 2019; Peng 2011; Gandrud 2014), which is a necessary requirement for the production of reliable knowledge.

Reproducibility projects in psychology and cancer biology are impacting current research practices across all domains. Examples of reproducible research are becoming more abundant in archaeology (Marwick 2016; Ivanovaite et al. 2020; Selden Jr., Dockall, and Shafer 2018; Selden Jr., Dockall, and Dubied 2020; Selden Jr et al. 2021a; Selden 2022), and the next generation of archaeologists are learning those tools and methods needed to reproduce and/or replicate research results (Marwick et al. 2019). Reproducible and replicable research work flows are often employed at the highest levels of humanities-based inquiries to mitigate concern or doubt regarding proper execution, and is of particular import should the results have—explicitly or implicitly—a major impact on scientific progress (Peels and Bouter 2018).

>>>>

Reproducibility—the ability to recompute results—and replicability—the chances other experimenters will achieve a consistent result—are two foundational characteristics of successful scientific research (Leek and Peng 2015). The analysis code associated with this project can be accessed through the [Supplementary Materials](https://seldenlab.github.io/elliptical.bifaces/), is available through the GitHub repository [https://github.com/seldenlab/elliptical.bifaces](https://github.com/seldenlab/elliptical.bifaces), and digitally curated on the Open Science Framework [DOI 10.17605/OSF.IO/PH25W](https://osf.io/ph25w/). The reproducible nature of this enterprise provides a means for others to critically assess and evaluate the various analytical components \citep{RN7434,RN7435,RN7427}, which is a necessary requirement for the production of reliable knowledge.

Reproducibility projects in psychology and cancer biology are impacting current research practices across all domains. Examples of reproducible research are becoming more abundant in archaeology \citep{RN9022,RN7818,RN10578,RN10576,RN8510,RN11097}, and the next generation of archaeologists are learning those tools and methods needed to reproduce and/or replicate research results \citep{RN10579}. Reproducible and replicable research work flows are often employed at the highest levels of humanities-based inquiries to mitigate concern or doubt regarding proper execution, and is of particular import should the results have—explicitly or implicitly—a major impact on scientific progress \citep{RN10580}.

### 2022-11-10 ms/ms/ms.tex
<edit ms>

Reproducibility---the ability to recompute results---and
replicability---the chances other experimenters will achieve a
consistent result---are two foundational characteristics of successful
scientific research (Leek and Peng 2015). The analysis code associated
with this project can be accessed through the
\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}, is available through the GitHub repository
\url{https://github.com/seldenlab/elliptical.bifaces}, and digitally
curated on the Open Science Framework \href{https://osf.io/ph25w/}{DOI
10.17605/OSF.IO/PH25W}. The reproducible nature of this enterprise
provides a means for others to critically assess and evaluate the
various analytical components (Gray and Marwick 2019; Peng 2011; Gandrud
2014), which is a necessary requirement for the production of reliable
knowledge.

Reproducibility projects in psychology and cancer biology are impacting
current research practices across all domains. Examples of reproducible
research are becoming more abundant in archaeology (Marwick 2016;
Ivanovaite et al.~2020; Selden Jr., Dockall, and Shafer 2018; Selden
Jr., Dockall, and Dubied 2020; Selden Jr et al.~2021a; Selden 2022), and
the next generation of archaeologists are learning those tools and
methods needed to reproduce and/or replicate research results (Marwick
et al.~2019). Reproducible and replicable research work flows are often
employed at the highest levels of humanities-based inquiries to mitigate
concern or doubt regarding proper execution, and is of particular import
should the results have---explicitly or implicitly---a major impact on
scientific progress (Peels and Bouter 2018).

>>>>

Reproducibility---the ability to recompute results---and
replicability---the chances other experimenters will achieve a
consistent result---are two foundational characteristics of successful
scientific research (Leek and Peng 2015). The analysis code associated
with this project can be accessed through the
\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}, is available through the GitHub repository
\url{https://github.com/seldenlab/elliptical.bifaces}, and digitally
curated on the Open Science Framework \href{https://osf.io/ph25w/}{DOI
10.17605/OSF.IO/PH25W}. The reproducible nature of this enterprise
provides a means for others to critically assess and evaluate the
various analytical components \citep{RN7434,RN7435,RN7427}, which is a
necessary requirement for the production of reliable knowledge.

Reproducibility projects in psychology and cancer biology are impacting
current research practices across all domains. Examples of reproducible
research are becoming more abundant in archaeology
\citep{RN9022,RN7818,RN10578,RN10576,RN8510,RN11097}, and the next
generation of archaeologists are learning those tools and methods needed
to reproduce and/or replicate research results \citep{RN10579}.
Reproducible and replicable research work flows are often employed at
the highest levels of humanities-based inquiries to mitigate concern or
doubt regarding proper execution, and is of particular import should the
results have---explicitly or implicitly---a major impact on scientific
progress \citep{RN10580}.
